Comparative Analysis of the wav2vec 2.0 Feature Extractor

### 2023-03-05 tables/features_pretraining.tex
update tables
tables: remove unused and add double lines

\centering
\caption{Effect of pre-training the wav2vec 2.0 feature extractor using the unsupervised loss on the same data (Librispeech 960h)}
\label{table:features_pretraining}
\begin{tabular}{|c|c|S|}
\hline
\multicolumn{2}{|c|}{Feature Extractor} &       {WER} \\\hline
                              Trainable & Pretrained & {dev-other} \\\hline
                                    yes &         no &         6.8 \\\cline{2-3}
                                        &        yes &         6.9 \\\cline{1-1}\cline{3-3}
                                     no &            &         7.1 \\
\hline
\end{tabular}

>>>>

\centering
\caption{Effect of pre-training the wav2vec 2.0 feature extractor using the unsupervised loss on the same data (Librispeech 960h).}
\label{table:features_pretraining}
\begin{tabular}{|c|c|S|}
\hline
\multicolumn{2}{|c|}{Feature Extractor} &       {WER} \\\hline
                              Trainable & Pretrained & {dev-other} \\\hline\hline
                                    yes &         no &         6.8 \\\cline{2-3}
                                        &        yes &         6.9 \\\cline{1-1}\cline{3-3}
                                     no &            &         7.1 \\
\hline
\end{tabular}
